Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-30 VMCAI-revised-version/final.tex
up

 \begin{center}
 	\begin{figure}
 	\hspace{-2.cm}
\includegraphics[width=1.40\textwidth]{All_results}
\caption{Hasse diagram of some classes of transition systems, together with the decidability (in green) or undecidability (in red) of the resilience problems. Decidability of bounded resilience and $k-$resilience variants are indicated in blue.}
	\end{figure}
\end{center}

@@

\begin{definition}(Finkel and Goubault-Larrecq \cite{DBLP:journals/corr/abs-1208-4549})
A WSTS  $\mathscr{S}=(S, \rightarrow, \leq)$
is an $\omega^2$-WSTS if $(S, \leq)$ is an $\omega^2$-wqo.
\end{definition}
Since almost of usual wqo are $\omega^2$-wqo, all naturally occurring WSTS are in fact $\omega^2$-WSTS: for example, reset/transfer VASS are $\omega^2$-WSTS.\\
%%%%%%

>>>>

 \begin{center}
 	\begin{figure}
 	\hspace{-2.cm}
\includegraphics[width=1.30\textwidth]{All_results}
\caption{ Hasse diagram of some classes of transition systems, together with the decidability (in green) or undecidability (in red) of the resilience problems. Decidability of bounded resilience and $k-$resilience variants are indicated in blue. Detailed notions of effectivity can be found on page~\pageref{on effectivity}. The different models are furthermore introduced in Section~2 and Section~3.}
	\end{figure}
\end{center}

\vspace{-0.5cm}

@@

\begin{definition}(Finkel and Goubault-Larrecq \cite{DBLP:journals/corr/abs-1208-4549})
A WSTS  $\mathscr{S}=(S, \rightarrow, \leq)$
is an $\omega^2$-WSTS if $(S, \leq)$ is an $\omega^2$-wqo.
\end{definition}
Since almost all usual wqo are $\omega^2$-wqo, all naturally occurring WSTS are in fact $\omega^2$-WSTS: for example, reset/transfer VASS are $\omega^2$-WSTS.\\
%%%%%%
